Flesh Simulation in the Field of Animation

### 2020-03-10 LaTeX-Master-Vorlage/chapter/Background.tex
background

\todoredefined[inline]{
TODO: Not done yet. Include determinant and what is used later
}

@@

\todoredefined[inline]{
TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end. Add Frobenius norm?
}

@@

The $\sigma_i$ denote the singular values of $\mathbf{\Sigma}$. Unlike the normal convention, the authors of \textit{\acrshort{snh}} decided that the rotation variant moves reflections to $\mathbf{\Sigma}$. This results in $\operatorname{det}(\mathbf{U})$ and $\operatorname{det}(\mathbf{V})$ being equal to 1 and the property that $\mathbf{\Sigma}$ is allowed to have negative entries.

\todoredefined[inline]{
TODO: Add some examples. Already include definitions of the paper?
\\ Some more sources:
\\ http://www.continuummechanics.org/deformationgradient.html
}

\subsubsection{Polar Decomposition of the Deformation Gradient}
With the help of Thm.\ref{PD} we can decompose the deformation gradient into the following form:

\[
\mathbf{F} = \mathbf{RS}.
\]

\todoredefined[inline]{
TODO: Explain more here.
}

>>>>

\todoredefined[inline]{
TODO: Not done yet. Include what is used later
}

@@

\subsection{Frobenius Norm}

\begin{definition}[\textbf{Frobenius Norm}]
\label{FN}
Let \textbf{A} be a (m $\times$ n) matrix in the real or complex space. Then the Frobenius norm is defined as 
\[
\| \mathbf{A} \|_{F} := \sqrt{\sum\limits_{i=1}^{m} \sum\limits_{j=1}^{n} |a_{ij}|^2}.
\]
\end{definition}

We can further represent the norm with the trace of the matrix, in which $\mathbf{A}^*$ is the conjugate transpose of \textbf{A}. Going from there, we can use the \acrshort{svd} of \textbf{A} and write the norm with respect to the singular values of \textbf{A}, denoted by $\sigma_i$
\[
\| \mathbf{A} \|_{F} = \sqrt{\operatorname{trace}(\mathbf{A} \mathbf{A}^*)} = \sqrt{\sum\limits_{i=1}^{\operatorname{min}\{m,n\}} \sigma_i^2}.
\]

\todoredefined[inline]{
TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end.
}

@@

The $\sigma_i$ denote the singular values of $\mathbf{\Sigma}$. Unlike the normal convention, \textbf{U} and \textbf{V} are rotations, which results in $\operatorname{det}(\mathbf{U})$ and $\operatorname{det}(\mathbf{V})$ being equal to 1. In addition, $\mathbf{\Sigma}$ is allowed to have negative entries.

\todoredefined[inline]{
TODO: Add some examples.
\\ Some more sources:
\\ http://www.continuummechanics.org/deformationgradient.html
}

\subsubsection{Polar Decomposition of the Deformation Gradient}
With the help of Thm.\ref{PD} we can decompose the deformation gradient into the following form
\[
\mathbf{F} = \mathbf{RS}
\]
where \textbf{R} is orthogonal and \textbf{S} is a positive definite symmetric matrix. \textbf{R} symbolises the rotation (with possible reflection) that \textbf{F} undergoes, whereas \textbf{S} contains the scaling along orthogonal directions of \textbf{F}.

\subsubsection{Relative volume change}

\subsubsection{Right Cauchy-Green}

\subsubsection{First right Cuachy-Green invariant}

### 2020-03-10 LaTeX-Master-Vorlage/chapter/paper.tex
background

\todoredefined[inline]{
TODO: include reflection convention? check with background
}

\subsection{The Complete Eigensystem}
\todoredefined[inline]{
TODO: Include what is necessary.
}

\todoredefined[inline]{
TODO: Make notation consistent (bold, cursive etc.) Explain better each step. Include all calculations? Make matrix of matrices more beautiful (more space). Eigenvalues of Mu and Gradient term better explain? Check each equation if correctly written.
}

>>>>

In order to investigate the behaviour of the volume Hessian term further, let us look at J = det(\textbf{F}) a bit more in detail. J is not convex which is problematic since we want to use the Newton method for the optimization process. Fortunately, the other terms of $\frac{\partial^2 \psi}{\partial \mathbf{F}^2}$ serve as an additional regularization.

\todoredefined[inline]{
TODO: include reflection convention? check with background. Regularisation?
}

\subsubsection{Volume Hessian Eigenvectors}
$\mathbf{\check{H}}$ can be factorized as $\mathbf{\check{H}} = \mathbf{\check{Q}}\mathbf{\Lambda}\mathbf{\check{H}}^\intercal$ according to its eigendecomposition. The eigenvectors can then be obtained by $\mathbf{\check{Q}}$. In the tensor form signified by $\mathbb{Q}$ each eigenvector is a 3 \times	 3 matrix:
\[
\mathbb{Q} = \left[\begin{array}{ccc}{\left[\mathbf{Q}_0\right]} & {\left[\mathbf{Q}_3\right]} & {\left[\mathbf{Q}_6\right]} \\ {\left[\mathbf{Q}_1\right]} & {\left[\mathbf{Q}_4\right]} & {\left[\mathbf{Q}_7\right]} \\ {\left[\mathbf{Q}_2\right]} & {\left[\mathbf{Q}_5\right]} & {\left[\mathbf{Q}_8\right]} \end{array}\right].
\]
The eigenvector corresponding to $\epsilon_3$ can be written as
\[
\mathbf{Q}_3 = \frac{1}{\sqrt{2}} \mathbf{U} \mathbf{D}_3 \mathbf{V}\intercal
\]
where \textbf{U} and \textbf{V} are taken from the \acrshort{svd} of \textbf{F}, $\frac{1}{\sqrt{•}}$

\subsection{The Complete Eigensystem}

\todoredefined[inline]{
TODO: Include what is necessary.
}

\todoredefined[inline]{
TODO: Eigenvalues of Mu and Gradient term better explain?
}
